---
title: "Matthew T. McBee's resume"
author: Matthew McBee
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
    css: ['css/custom_resume.css', 'css/styles.css', 'resume']
---

```{r, include=F}
library(glue)
library(dplyr)
library(here)
library(plotBayes)
```


```{r, include=F}
par(bg=NA) 
set.seed(1)
data <- rnorm(n=10, mean=1, sd=1)
plot.new()
plotBayes(data, prior.type="normal", prior.parameters=c(0, .5), min=-2, max=2) 

p <- recordPlot()
dev.off()
```


Aside
================================================================================

```{r, echo=F}
p
```




Contact Info {#contact}
--------------------------------------------------------------------------------

- <i class="fa fa-envelope"></i> mmcbee@gmail.com
- <i class="fa fa-github"></i> [github.com/mcbeem](https://github.com/mcbeem)
- <i class="fa fa-spinner"></i> [https://osf.io/nwd3a/](https://osf.io/nwd3a/)
- <i class="fa fa-twitter"></i> [TunnelofFire](https://twitter.com/TunnelOfFire)
- <i class="fa fa-phone"></i> +1 919-943-7204


Skills {#skills}
--------------------------------------------------------------------------------

- Data science, statistical analysis, machine learning, reproducible computing, Bayesian methods, open science, technical writing, presentation

- Highly skilled in R, R Markdown, ggplot2, Shiny, Tidyverse, SAS, Stata, MPlus, LaTeX

- Expertise in complex data structures, reproducible computing, statistical programming, R package development, causal inference, psychometrics


Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

This resume was made with the R package [**pagedown**](https://github.com/rstudio/pagedown).

Last updated on `r Sys.Date()`.

Main
================================================================================

Matthew McBee {#title}
--------------------------------------------------------------------------------

Professional Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

### Assistant / Associate Professor of Quantitative Psychology

East Tennessee State University

Johnson City, TN

2011 -

- Tenured & Promoted to Associate Professor in 2016
- Program Director, Experimental Psychology Ph.D program
- Teaches statistics, research methods, and statistical programming

### Statistician / Investigator

Frank Porter Graham Child Development Institute  
University of North Carolina - Chapel Hill

Chapel Hill. NC

2008 - 2011



- Statistical consulting
- Study design
- Data analysis
- Grant proposal preparation
- Statistical programming

### Research and Evaluation Specialist

University of North Carolina - General Administration

Chapel Hill, NC

2006 - 2008

- Evaluation design
- Survey construction
- Database queries and reports
- Data cleaning
- Scripting

Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

### The University of Georgia

Ph.D. in Educational Psychology

Athens, GA

2006

### The University of Georgia

M.Ed. in Educational Psychology

Athens, GA

2004

### Tennessee Technological University

B.S. in Psychology (Honors)

Cookeville, TN

2002


R packages {data-icon=file}
--------------------------------------------------------------------------------

### giftedCalcs

A package for gifted identification psychometrics. Implements calculations from equations derived in McBee et al. (2016) and in ongoing work. [https://github.com/mcbeem/giftedCalcs](https://github.com/mcbeem/giftedCalcs)

N/A

N/A

### regSim

A package for simple and quick statistical simulation. [https://github.com/mcbeem/regsim](https://github.com/mcbeem/regsim)

N/A

N/A

### plotBayes

A package illustrating the principles of Bayesian inference. [https://github.com/mcbeem/plotBayes](https://github.com/mcbeem/plotBayes)

N/A

N/A

### ZPDGrowthTrajectories

A package for creating and exploring synthetic growth trajectories based on a theoretical model of academic achievement. 
[https://github.com/mcbeem/ZPDGrowthTrajectories](https://github.com/mcbeem/ZPDGrowthTrajectories)

N/A

N/A

Selected shiny apps {data-icon=file}
--------------------------------------------------------------------------------

### Critical values and sampling distribution under the null 

[https://mmcbee.shinyapps.io/critical_values/](https://mmcbee.shinyapps.io/critical_values/)

N/A

N/A

### Exact p-value calculator for normal, *t*, *F*, and chi-squared statistics

[https://mmcbee.shinyapps.io/shiny_p_values/](https://mmcbee.shinyapps.io/shiny_p_values/)

N/A

N/A

### Gifted program identification psychometrics explorer

[https://mmcbee.shinyapps.io/gifted_identification_explorer/](https://mmcbee.shinyapps.io/gifted_identification_explorer/)

N/A

N/A

Selected Publications {data-icon=file}
--------------------------------------------------------------------------------

I have authored two books (1 currently in press), 43 articles in peer-reviewed journals, and delivered 99 presentations at scientific meetings, including two keynote addresses.  


```{r, results="asis", echo=F}
papers <- read.csv("citations.csv", stringsAsFactors=F, header=T)

papers %>%
  filter(Include==1) %>%
  glue_data(
   "### {Title}", "\n\n",
   "{Publication}. {Pages}", "\n\n",
   "N/A", "\n\n",
   "{Year}", "\n\n",
   "\n\n",
   "{Authors}",
   "\n\n\n"
 )

# papers %>% 
#   filter(Include==1) %>%
#   glue_data(
#    "-{Authors}. ({Year}). {Title}. ", 
#    "*{Publication}*. *{Volume}*({Number}). {Pages}, {DOI}", 
#    "\n\n", sep=""
#  )
```
